---
title: "Netflix-blogpost"
author: "MG"
date: "5/18/2020"
output:
  word_document: default
  html_document: default
---
In this blog post, I will show some basic data cleaning methods, organization of data frame and data visualization using [netflix movies and tv show dataset](https://www.kaggle.com/shivamb/netflix-shows) from Kaggle.com.

# R Markdown : importing data

Data from real world are always unstructured. So, to make it usable we need to organize it. It is probably one of the most time-consuming and unpopular aspect of data-analysis.



```{r}
netflix_titles <- read.csv("C:/Users/moumi/Desktop/netflix_titles.csv", na.strings=c("","NA"))

```

# Find missing values and removing them

```{r}

sapply(netflix_titles, function(x) sum(is.na(x)))
data_new <- na.omit(netflix_titles)
library(tidyr)
cleandata <- netflix_titles %>% drop_na(country,date_added )

```


# data visualization : pie : content type

```{r}
library(ggplot2)
library(ggplot2)
theme_set(theme_classic())
library(ggplot2)
library(ggpubr)
theme_set(theme_pubr())


ggplot(netflix_titles, aes(netflix_titles$type)) +
  geom_bar(fill = "#0073C2FF") +
  theme_pubclean()
```


```{r}
library(dplyr)
df <- netflix_titles %>%
  group_by(type) %>%
  summarise(counts = n())
df

ggplot(df, aes(x = df$type, y = counts)) +
  geom_bar(fill = "#0073C2FF", stat = "identity") +
  geom_text(aes(label = counts), vjust = -1) + 
  theme_pubclean()

#pie

data(df)

df1 <- df %>%
       mutate(prop = round(df$counts*100/(sum(df$counts)), 1))
              head(df1, 4)

ggplot(df1, aes(x = "", y = prop, fill = df1$type)) +
  geom_bar(width = 1, stat = "identity", color = "white") + 
  labs(x = NULL, y = NULL, fill = NULL, title = "Content type") +
  geom_text(aes(label = prop), color = "white", vjust = -3)+
  coord_polar("y", start = 0)+
  scale_fill_manual(values = c("#ffd700", "#bcbcbc", "#ffa500", "#254290")) +
  theme_classic() +
  theme(axis.line = element_blank(),
            axis.text = element_blank(),
            axis.ticks = element_blank(),
            plot.title = element_text(hjust = 0.5, color = "#666666"))
```

#year released
```{r}
library(dplyr)
df <- netflix_titles %>%
  group_by(release_year) %>%
  summarise(counts = n())
df

ggplot(df, aes(x = df$release_year, y = counts)) +
  geom_bar(fill = "#ffd700", stat = "identity") +
  labs(x = "Year", y = "Number of movies/TV series released", fill = NULL, title = NULL, tag="Figure 2", vjust= -3) +
  theme_pubclean()

```
#no of movie tv by year

```{r}
#splitting the date column

library(stringr)
date.df <- as.data.frame(str_match(cleandata$date_added, "^(.*) (.*),(.*)$")[,-1])
df.new <- cbind.data.frame(cleandata, date.df)

library(dplyr)
df2 <- df.new %>%
  group_by(V3) %>%
  summarise(counts = n())
df2

ggplot(df2, aes(x = df2$V3, y = counts)) +
  geom_bar(fill = "#ffd700", stat = "identity") +
  geom_line(group=1, color="#bcbcbc") +
  geom_point()+
  labs(x = "Year", y = "Number of movies/TV series added", fill = NULL, title = NULL, tag="Figure 3", vjust= 1) +
  theme_pubclean()
```

#content by year and type

```{r}

#use df.new from now on. cleandata is the right data. I used cleandata to find out df.new.


ggplot(df.new, 
       aes(x = df.new$V3, 
           fill = type)) + 
  geom_bar(position = "stack") +
  scale_fill_manual(values = c("#bcbcbc","#ffd700")) +
  labs(y = "Number of Movies/TV shows", 
       fill = "Content type",
       x = "Year") +
  theme_pubclean()

#create summary

library(dplyr)
plotdata <- df.new %>%
  group_by(df.new$V3, df.new$type) %>%
  summarize(n = n()) %>% 
  mutate(pct = n/sum(n),
         lbl = scales::percent(pct))
plotdata

ggplot(plotdata, 
       aes(x = factor(df.new$V3),
           y = pct,
           fill = factor(df.new$type))) + 
  geom_bar(stat = "identity",
           position = "fill") +
  scale_y_continuous(breaks = seq(0, 1, .2), 
                     label = percent) +
  geom_text(aes(label = lbl), 
            size = 3, 
            position = position_stack(vjust = 0.5)) +
  scale_fill_brewer(palette = "Set2") +
  labs(y = "Percent", 
       fill = "Drive Train",
       x = "Class",
       title = "Automobile Drive by Class") +
  theme_minimal()
```

# map of countries

```{r}
cleandata %>% group_by(type) %>% mutate(country = fct_infreq(country)) %>% ggplot(aes(x = country)) + 
            geom_histogram(stat = 'count') + 
            facet_wrap(~type, scales = 'free_x') + 
            theme_pubclean() +
            scale_fill_manual(values = "red")+
            coord_cartesian(xlim = c(1,5)) + scale_x_discrete(labels = function(x){str_wrap(x,20)}, breaks = function(x) {x[1:8]})
```

